Topological Equivariant Artist Model

### 2021-12-29 slides/main.tex
sheaf equation
breakdown of bundle
reworked functors

\begin{frame}{Fiber Bundles}
    \begin{columns}
        \column{0.39\textwidth}
            \begin{equation*}
                %\label{eq:related-work:continuity:fiber-bundle}
                \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
                  \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
                   \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
                \end{tikzcd}
            \end{equation*}
     \column{0.59\textwidth}
        \begin{description}
            \item[\textcolor{base}{Base Space}] $( \dbasec, \mathcal{T})$ with
                \begin{itemize}
                   \item open sets $\opensetc \subset \dbasec$
                   \item points $\dbasepointc \in \opensetc \in \dbasec$
                 \end{itemize}  
            \item[\textcolor{fiber}{Fiber Space}] $\dfiberc_{\dbasepointc} = \pi^{-1}(\dbasepointc)$
            \item[\textcolor{total}{Total Space}]  $\dtotalc\restriction_{\opensetc} = \dbasec\restriction_{\opensetc} \times \dfiberc\restriction_{\opensetc}$ \\ for all $\opensetc \subset K$ 
        \end{description}
    \end{columns}
    \pause
    \begin{alertblock}{Sections}
    $\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \dtotalc\restriction_{\openset} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\}$
    \end{alertblock}
\end{frame}

\begin{frame}{Category $\textcolor{source}{\mathcal{C}}$}
\begin{columns}
    \column{0.39\textwidth}
\begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \textcolor{source}{C_1} \arrow[r, "f", color=source] \arrow[rd, "g\circ f"', color=source] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source] \& \textcolor{source}{C_2} \arrow[d, "g", color=source] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source] \\
    \& \textcolor{source}{C_3} \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]              
    \end{tikzcd}
    \end{equation*}
    \column{0.59\textwidth}
    \begin{alertblock}{associativity} 
        if $f: C_1 \rightarrow C_2$, $g: C_2 \rightarrow C_3$ and $h: C_3 \rightarrow C_4$ then $h\circ (g \circ f) = (h \circ g) \circ f$
    \end{alertblock}
    \begin{alertblock}{identity} 
        for every $f: C_1 \rightarrow C_2$ there exists identity morphisms $f \circ id_{C_1} = f = id_{C_2} \circ f$
    \end{alertblock}
    \end{columns}
\end{frame}

@@

\begin{frame}{Functor $\textcolor{sheaf}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \textcolor{source}{c} \arrow[d, "f"', shift right=0, color=source] \arrow[r, "F", color=functor] \& \textcolor{target}{F(c)} \arrow[d, "F(f)", shift right=0, color=target] \\
            \textcolor{source}{c^{\prime}} \arrow[r, "F"', color=functor]                       \& \textcolor{target}{F(c^{\prime})}                      
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}{composition}
    $\textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})$
    \end{alertblock}
    \begin{alertblock}{identity}
    $\textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}$
    \end{alertblock}
\end{columns}
\end{frame}

\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\rightarrow} \textcolor{functor}{G}$}

\begin{frame}{Subsets?}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {} \& {} \& \\\& \&\\
            \opensetc_1 \subset \dbasec \arrow[uu, "", color=white] \& {}  \&                    
            \end{tikzcd}
    \end{columns}
\end{frame}

\begin{frame}{Subsets?}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} \& {} \& \\\& \&\\
            \opensetc_1 \subset \dbasec \arrow[uu, "", color=white] \& {}  \&                    
            \end{tikzcd}
    \end{columns}
\end{frame}

@@

\begin{frame}{Sheaf}

\begin{comment}
\subsection{Contributions}
\begin{frame}{Contributions}
    \begin{description}
        \item[Topological] continuity  
        \item[Equivariant] monoid action 
        \item[Artist] Matplotlib $\textit{artist}: \textit{data} \rightarrow \textit{graphic}$ 
        \item [Model] 
    \end{description}
\end{frame}

>>>>

\begin{frame}{Fiber Bundles}
    \begin{columns}
        \column{0.39\textwidth}
            \begin{equation*}
                %\label{eq:related-work:continuity:fiber-bundle}
                \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
                  \onslide*<2-|handout:2->{\dfiberc} \onslide*<4-|handout:4->{\arrow[r, hook]} \& \onslide*<3|handout:3->{\dtotalc} \onslide*<4-|handout:4->{\arrow[d, "\pi"']} \\
                   \& \onslide*<1-|handout:1->{\dbasec} \onslide*<5-|handout:5->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
                \end{tikzcd}
            \end{equation*}
     \column{0.59\textwidth}
        \begin{description}
            \item<1-|handout:1->[\textcolor{base}{Base Space}] $( \dbasec, \mathcal{T})$, $\dbasepointc \in \opensetc \subset \dbasec$
            \item<2-|handout:2->[\textcolor{fiber}{Fiber Space}] $\dfiberc_{\dbasepointc} = \pi^{-1}(\dbasepointc)$
            \item<3-|handout:3->[\textcolor{total}{Total Space}]  $\dtotalc\restriction_{\opensetc} = \dbasec\restriction_{\opensetc} \times \dfiberc\restriction_{\opensetc}$ \\ for all $\opensetc \subset K$ 
        \end{description}
    \end{columns}
    \pause
    \begin{alertblock}<5-|handout:5->{Sections}
    $\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \dtotalc\restriction_{\openset} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\}$
    \end{alertblock}
\end{frame}

\subsection{Category Theory}
\begin{frame}{Category $\textcolor{source}{\mathcal{C}}$}
\begin{columns}
    \column{0.39\textwidth}
\begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \textcolor{source}{C_1} \arrow[r, "f", color=source] \arrow[rd, "g\circ f"', color=source] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source] \& \textcolor{source}{C_2} \arrow[d, "g", color=source] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source] \\
    \& \textcolor{source}{C_3} \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]              
    \end{tikzcd}
    \end{equation*}
    \column{0.59\textwidth}
    \begin{alertblock}{associativity} 
        if $f: C_1 \rightarrow C_2$, $g: C_2 \rightarrow C_3$ and $h: C_3 \rightarrow C_4$ then $h\circ (g \circ f) = (h \circ g) \circ f$
    \end{alertblock}
    \begin{alertblock}{identity} 
        for every $f: C_1 \rightarrow C_2$ there exists identity morphisms $f \circ id_{C_1} = f = id_{C_2} \circ f$
    \end{alertblock}
    \end{columns}
\end{frame}
\begin{frame}{Category $\mathcal{\dbasec}$}
\begin{columns}
    \column{0.49\textwidth}
\begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \textcolor{source}{C_1} \arrow[r, "f", color=source] \arrow[rd, "g\circ f"', color=source] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source] \& \textcolor{source}{C_2} \arrow[d, "g", color=source] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source] \\
    \& \textcolor{source}{C_3} \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]              
    \end{tikzcd}
    \end{equation*}
    \column{0.49\textwidth}
    \onslide<2-|handout:2->{
    \begin{tikzcd}[ampersand replacement=\&]
            \opensetc_1 \arrow[r, "\iota_{1,2}", color=base] \arrow[rd, "\iota_{1,2}\circ \iota_{2,3}"', color=base] \arrow["id_{\opensetc_1}"', loop, distance=2em, in=215, out=145, color=base] \& \opensetc_2 \arrow[d, "\iota_{2,3}", color=base] \arrow["id_{\opensetc_2}"', loop, distance=2em, in=125, out=55, color=base] \\
        \& \opensetc_3 \arrow["id_{\opensetc_3}"', loop, distance=2em, in=305, out=235, color=base]              
    \end{tikzcd}
    }
    \end{columns}
\end{frame}

@@

\begin{frame}{$\mathcal{C}^{op}$ with Objects of \setc}
    \begin{columns}
        \column{0.29\textwidth}
        \begin{tikzcd}[ampersand replacement=\&]
            \opensetc_1 \arrow[r, "\iota_{1,2}", color=base] \arrow[rd, "\iota_{1,2}\circ \iota_{2,3}"', color=base] \arrow["id_{\opensetc_1}"', loop, distance=2em, in=215, out=145, color=base] \& \opensetc_2 \arrow[d, "\iota_{2,3}", color=base] \arrow["id_{\opensetc_2}"', loop, distance=2em, in=125, out=55, color=base] \\
        \& \opensetc_3 \arrow["id_{\opensetc_3}"', loop, distance=2em, in=305, out=235, color=base]              
    \end{tikzcd}
        \column{0.69\textwidth}
        \onslide<2-|handout:2->{
            \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc_1}{\dtotalc\restriction_{\opensetc_1}} \&  \& \cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}} \arrow[ll, "\iota^*\restriction_{\opensetc_1}"', color=set]\\
            \&\&\\\&  \& \cgamma{\opensetc_3}{\dtotalc\restriction_{\opensetc_3}} \arrow[uu, "\iota^*\restriction_{\opensetc_2}"', color=set] \arrow[lluu, "\iota^*\restriction_{\opensetc_2} \circ \iota^*\restriction_{\opensetc_1}", color=set]
            \end{tikzcd}

        }

        \end{columns}
\end{frame}

\begin{frame}{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1->{\textcolor{source}{c}} 
            \onslide*<1-|handout:1->{\arrow[d, "f"', shift right=0, color=source]} \onslide*<3-|handout:3->{\arrow[r, "F", color=functor]} \& 
            \onslide*<2|handout:2>{\textcolor{target}{d}}
            \onslide*<3-|handout:3->{\textcolor{target}{F(c)}} 
            \onslide*<2|handout:2>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:3->{\arrow[d, "F(f)", shift right=0, color=target]} \\
            \onslide*<1-|handout:1->{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:3->{\arrow[r, "F"', color=functor]}\& 
            \onslide*<2|handout:2>{\textcolor{target}{d^{\prime}}}
            \onslide*<3-|handout:3->{\textcolor{target}{F(c^{\prime})}}                      
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<4-|handout:4->{composition}
    $\textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})$
    \end{alertblock}
    \begin{alertblock}<5-|handout:5->{identity}
    $\textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}$
    \end{alertblock}
\end{columns}
\end{frame}

\begin{frame}{Presheaf on Bundle: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {} \& {} \& \\\& \&\\
            \opensetc_1 \subset \dbasec \arrow[uu, "", color=white] \& {}  \&                    
            \end{tikzcd}
    \end{columns}
\end{frame}

\begin{frame}{Presheaf on Bundle: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} \& {} \& \\\& \&\\
            \opensetc_1 \subset \dbasec \arrow[uu, "", color=white] \& {}  \&                    
            \end{tikzcd}
    \end{columns}
\end{frame}

@@

\begin{frame}{Sheaves}
    A sheaf is a presheaf that satisfies the following two axioms

    \onslide<2-|handout:2->{Given open cover $\mathcal{\opensetc} = \{\opensetc_i\}_{i\in I}$ of $\opensetc$:}
    \begin{block}<3-|handout:3->{locality}
    $\dsectionc^{1}, \dsectionc^{2} \in \sheafc(\opensetc_i)\\ \dsectionc^{1}\restriction_{\opensetc_i} = \dsectionc^{2}\restriction_{\opensetc_i} \implies \dsectionc^{1} = \dsectionc^{2}$
    \end{block} 
    \begin{block}<4-|handout:4>{gluing}
    $\dsectionc_{i} \in \sheafc(\opensetc_i), \dsectionc_{j} \in \sheafc(\opensetc_j), \opensetc_i, \opensetc_j \in \mathcal{U}\\ \dsectionc_{i}\restriction_{\opensetc_i\cap \opensetc_j} = \dsectionc_{j}\restriction_{\opensetc_i \cap \opensetc_j} \implies \dsectionc\restriction_{\opensetc_i} = \dsectionc_i$ 
    \end{block}    
\end{description}    
\end{frame}

\subsubsection{Sheaves}
\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\rightarrow} \textcolor{functor}{G}$}

\begin{comment}

\subsection{Contributions}
\begin{frame}{Contributions}
    \begin{description}
        \item[Topological] continuity  
        \item[Equivariant] monoid action 
        \item[Artist] Matplotlib $\textit{artist}: \textit{data} \rightarrow \textit{graphic}$ 
        \item [Model] 
    \end{description}
\end{frame}
